---
title: "WriteUp Linear Model (current)"
author: "Matthew Ramirez"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model1: SIMS-ARM
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5,size = 20))
```

## Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

## Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

## Create Target

```{r}
target <- data.frame(ARM=90, GRIP=90)
```

## Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

## Linear Fill Model1

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5,size = 20)) + geom_smooth(method=lm)
```

## Model2: SIMS~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5,size = 20))
```

## Numerical Results Model2

```{r}
cor(SIMS~GRIP,data=data)
```

## Inferential Results Model2

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

## Predict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

## Linear Fill Model2

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5,size = 20)) + geom_smooth(method=lm)
```

## Model3: SIMS~ARM+GRIP



## Numerical Results Model3

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number for model3 (SIMS~ARM+GRIP) is higher compared to model2 (SIMS~GRIP) and model1 (SIMS~ARM), so the correlation is better when using both models (ARM and GRIP) rather than using one of them (either ARM or GRIP).

## Inferential Results Model3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```











